---
output: github_document
always_allow_html: true
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# datavolleyXtra

<!-- badges: start -->

<!-- badges: end -->

datavolleyXtra is a supplementary to <https://github.com/openvolley/datavolley>.

## Installation

You can install the development version of datavolleyXtra from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("tyler-widdison/datavolleyXtra")
```

## Reading datavolley files

This `dv_readXtra` is a function to read datavolley files with additional columns. Add as many files as you want so long as you have the correct path.

```{r datavolley}
library(datavolleyXtra)
df <- dv_readXtra("dvws")
df %>% head()
```

Return a reception data table:

`rec_table(df, 'Iowa', 3)`

## Get NCAA Women's Volleyball schedules

Get the NCAA womens teams

```{r teams}
get_ncaaw_teams()
```

Get NCAA womens team or conference schedule

```{r teamSchedule}
get_team_schedule(team_name = 'Yale', team_id = '813', yr = 2019)
```

```{r confSchedule}
get_conf_schedule(conf_name = 'Big Ten', yr = 2022)
```
